\vspace{-0.5in}{\bfseries\scshape Transfer Learning for computationally limited training of Vision Transformers on art classification tasks } \\ \vspace{1ex} \normalsize{Bachelor's Project Thesis}\vspace{-2ex}

### 2022-07-20 writing/report.tex
working on the presentation
Continued working on writing y paper
Rewriting results section -> Now its an 'Experiments' section with 'Results' subsection. Some small tweaks as well
Finished the results section and made some progress with the Interpretation/Discussion section
Slowly getting there.. Still working on the 'discussion' section. Also started writing the conclusion.
Concusion concluded.
Finished the abstract earlier today. With that, the first draft is done!

\title{\vspace{-0.5in}{\bfseries\scshape 
    Transfer Learning for computationally limited training of Vision Transformers on art classification tasks
    } \\ 
    \vspace{1ex} 
    \normalsize{Bachelor's Project Thesis}\vspace{-2ex}
}

\author{
    \normalsize{V. Tonkes, s3617157, v.tonkes@student.rug.nl,} \\ 
    \normalsize{Supervisor: Dr. M. Sabatelli}
}

@@

\twocolumn[
  \maketitle
  \begin{@twocolumnfalse}
%   \input{./tex/abstract.tex}
  \end{@twocolumnfalse}
]

@@

\input{tex/draft_introduction.tex}
\input{tex/draft_methods.tex}
\input{tex/draft_results.tex}

@@

>>>>

%\widowpenalties 1 10000
\raggedbottom

\title{\vspace{-0.5in}{\bfseries\scshape 
    Transferability of Vision Transformers: The key to success on small art classification datasets?%    Transfer Learning for computationally limited training of Vision Transformers on art classification tasks
    } \\ 
    \vspace{1ex} 
    \normalsize{Bachelor's Project Thesis}\vspace{-2ex}
}

\author{
    \normalsize{V. Tonkes, s3617157, v.tonkes@student.rug.nl,} \\ 
    \normalsize{Supervisor: M. Sabatelli, PhD}
}

@@

\twocolumn[
  \maketitle
  \begin{@twocolumnfalse}
   \input{tex/draft_abstract.tex}
  \end{@twocolumnfalse}
]

@@

\input{tex/draft_introduction.tex}
\input{tex/draft_methods.tex}
\input{tex/draft_experiments.tex}
\input{tex/draft_conclusion.tex}

\section*{Acknowledgements}
\textit{The author would like to thank {the Center for Information Technology of the University of Groningen} for their support and for providing access to the Peregrine high performance computing cluster. He would also like to thank {dr. M. Sabatelli} for his guidance during this project.}

@@

%\clearpage
